\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-08-29 jss/article.tex
edit3

The overall RB unbiased coverage estimate across all the hospitals is 0.955. And none of RB unbiased coverage estimates for 31 hospitals are less than 0.95 regardless of their caseloads ($n_{j}$). This result shows that the interval estimates for this particular dataset accurately achieves 95\% confidence under repeated sampling. Note that these estimates depend on the given true value of $r$, the known prior mean, and the assumption that the model is true.

The following code provides 31 RB unbiased coverage estimates for each hospital.
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.956 0.957 0.956 0.956 0.956 0.956 0.956 0.956 0.956 0.956 0.956 0.955 
[13] 0.955 0.956 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.954 0.955 0.955 
[25] 0.955 0.954 0.954 0.954 0.954 0.953 0.953
\end{CodeOutput}
\end{CodeChunk}

And the code below calculates 31 simple unbiased coverage estimates for each hospital.
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$coverageS
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.955 0.959 0.955 0.949 0.944 0.955 0.960 0.947 0.948 0.962 0.967 0.962 
[13] 0.957 0.959 0.961 0.958 0.957 0.948 0.963 0.963 0.967 0.955 0.968 0.948 
[25] 0.965 0.947 0.955 0.946 0.957 0.948 0.948
\end{CodeOutput}
\end{CodeChunk}

The function \code{coverage} also calculates the standard errors for each hospital's RB unbiased coverage estimate defined as the square root of $S^{2}_{RB, j}/N_{sim}$, where $S^{2}_{RB, j}$ is the sample variance of 1,000 RB unbiased coverage estimates for the $j$-th hospital. The following code provides 31 standard errors.
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$se.coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.0015 0.0015 0.0013 0.0012 0.0012 0.0012 0.0012 0.0012 0.0011 0.0011 0.0011 
[12] 0.0011 0.0010 0.0010 0.0010 0.0010 0.0011 0.0010 0.0010 0.0010 0.0009 0.0010 
[23] 0.0009 0.0009 0.0009 0.0009 0.0008 0.0008 0.0007 0.0006 0.0006
\end{CodeOutput}
\end{CodeChunk}
Similarly, 31 standard errors for each simple unbiased coverage estimate are
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$se.coverageS
\end{CodeInput}
\begin{CodeOutput}
[1] 0.0063 0.0060 0.0071 0.0063 0.0059 0.0066 0.0063 0.0068 0.0060 0.0076 0.0063 
[12] 0.0059 0.0066 0.0072 0.0070 0.0074 0.0060 0.0062 0.0065 0.0065 0.0075 0.0072 
[23] 0.0061 0.0067 0.0064 0.0065 0.0061 0.0072 0.0067 0.0070 0.0065
\end{CodeOutput}
\end{CodeChunk}

Taking the first hospital as an example, the variance of RB unbiased coverage estimate is about 18 times smaller than that of simple one. It means that 1,000 RB unbiased coverage estimates are as precise as 18,000 simple unbiased coverage estimates in terms of estimating true coverage probability for the first hospital.

@@

In addition, Rao-Blackwellized (RB) unbiased coverage estimates for each school can be gotten with the command below.
\begin{CodeChunk}
\begin{CodeInput}
R> gcv$coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.966 0.957 0.966 0.962 0.960 0.961 0.960 0.969
\end{CodeOutput}
\end{CodeChunk}

@@

The Rao-Blackwellized unbiased coverage estimates and their standard errors for each player follow.
\begin{CodeChunk}
\begin{CodeInput}
R> bcv$coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.972 0.972 0.973 0.972 0.972 0.970 0.974 0.972 0.973 0.973 0.973 0.970 
[13] 0.972 0.972 0.973 0.972 0.973 0.972
\end{CodeOutput}
\end{CodeChunk}
\begin{CodeChunk}
\begin{CodeInput}
R> bcv$se.coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.0012 0.0013 0.0012 0.0012 0.0013 0.0011 0.0011 0.0009 0.0012 0.0013 
[11] 0.0010 0.0013 0.0010 0.0012 0.0015 0.0010 0.0010 0.0011
\end{CodeOutput}
\end{CodeChunk}

>>>>

The overall RB unbiased coverage estimate across all the hospitals is 0.954. And none of RB unbiased coverage estimates for 31 hospitals are less than 0.95 regardless of their caseloads ($n_{j}$). This result shows that the interval estimates for this particular dataset accurately achieves 95\% confidence under repeated sampling. Note that these estimates depend on the given true value of $r$, the known prior mean, and the assumption that the model is true.

The following code provides 31 RB unbiased coverage estimates for each hospital.
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.954 0.954 0.955 
[13] 0.954 0.955 0.954 0.954 0.954 0.955 0.954 0.954 0.954 0.954 0.954 0.954 
[25] 0.953 0.954 0.953 0.953 0.954 0.952 0.952
\end{CodeOutput}
\end{CodeChunk}

And the code below calculates 31 simple unbiased coverage estimates for each hospital.
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$coverageS
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.960 0.953 0.956 0.952 0.957 0.957 0.960 0.949 0.949 0.944 0.951 0.947 
[13] 0.949 0.958 0.958 0.959 0.953 0.954 0.953 0.955 0.956 0.952 0.953 0.959 
[25] 0.945 0.945 0.953 0.946 0.953 0.948 0.955
\end{CodeOutput}
\end{CodeChunk}

The function \code{coverage} also calculates the standard errors for each hospital's RB unbiased coverage estimate defined as the square root of $S^{2}_{RB, j}/N_{sim}$, where $S^{2}_{RB, j}$ is the sample variance of 1,000 RB unbiased coverage estimates for the $j$-th hospital. The following code provides 31 standard errors.
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$se.coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.0016 0.0016 0.0014 0.0013 0.0013 0.0013 0.0013 0.0013 0.0013 0.0013 0.0012 
[12] 0.0012 0.0012 0.0011 0.0011 0.0011 0.0011 0.0011 0.0011 0.0011 0.0011 0.0010
[23] 0.0010 0.0010 0.0010 0.0009 0.0009 0.0008 0.0008 0.0007 0.0007
\end{CodeOutput}
\end{CodeChunk}
Similarly, 31 standard errors for each simple unbiased coverage estimate are
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$se.coverageS
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.0062 0.0067 0.0065 0.0068 0.0064 0.0064 0.0062 0.0070 0.0070 0.0073 0.0068 
[12] 0.0071 0.0070 0.0063 0.0063 0.0063 0.0067 0.0066 0.0067 0.0066 0.0065 0.0068
[23] 0.0067 0.0063 0.0072 0.0072 0.0067 0.0072 0.0067 0.0070 0.0066
\end{CodeOutput}
\end{CodeChunk}

Taking the first hospital as an example, the variance of RB unbiased coverage estimate is about 15 times smaller than that of simple one. It means that 1,000 RB unbiased coverage estimates are as precise as 15,000 simple unbiased coverage estimates in terms of estimating true coverage probability for the first hospital.

@@

In addition, Rao-Blackwellized (RB) unbiased coverage estimate and its standard error for each school can be gotten with the command below.
\begin{CodeChunk}
\begin{CodeInput}
R> gcv$coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.964 0.958 0.964 0.960 0.956 0.959 0.958 0.966
\end{CodeOutput}
\end{CodeChunk}
\begin{CodeChunk}
\begin{CodeInput}
R> gcv$se.coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.0014 0.0013 0.0016 0.0014 0.0014 0.0012 0.0012 0.0017
\end{CodeOutput}
\end{CodeChunk}

@@

The Rao-Blackwellized unbiased coverage estimates and their standard errors for each player follow.
\begin{CodeChunk}
\begin{CodeInput}
R> bcv$coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.973 0.973 0.974 0.971 0.971 0.973 0.972 0.973 0.972 0.973 0.971 0.973 
[13] 0.971 0.972 0.974 0.972 0.972 0.973
\end{CodeOutput}
\end{CodeChunk}
\begin{CodeChunk}
\begin{CodeInput}
R> bcv$se.coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.0010 0.0011 0.0011 0.0013 0.0012 0.0011 0.0012 0.0011 0.0012 0.0010 
[11] 0.0013 0.0012 0.0013 0.0013 0.0010 0.0010 0.0010 0.0010
\end{CodeOutput}
\end{CodeChunk}
